A Vignetted View of Computer Science through Citation Analysis

### 2019-12-17 Scientometrics/comp.tex
udpate

\subsection{Data}
The process of selection and matching resulted in a dataset of  publications (Materials and Methods). Of 4,291,130 DBLP publications with DOIs, only  2,685,356 are found in Scopus. Of these roughly 2.8 million publications, approximately 2.07 million were classified in Scopus as COMP under subject area and assigned ASJC codes corresponding to Computer Science (major subject area with 13 minor subject areas (Table~\ref{tab:comp}), with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (Fig.~\ref{fig:ar_cp_annotation}). The set of 2.07 million publications classified under the major subject area Computer Science in Scopus spanned all 13 minor subject areas with Software 30.3\% being the largest component and Computer Science (miscellaneous) 0.9\% the smallest (Table~\ref{tab:comp}). Another 409,082  publications were labeled Theoretical Computer Science under the major subject area of Mathematics. 38.86\% of the publications were assigned to one minor subject area, 78.1\% to two minor subject areas, 909.9\% to three minor subject areas, and 0.0003\% assigned to 8 different minor subject areas.

>>>>

\subsection{Data}
The process of selection and matching resulted in a dataset of  publications (Materials and Methods). Of 4,291,130 DBLP publications with DOIs, only  2,685,356 had corresponding DOIs in Scopus. Of these roughly 2.68 million publications, approximately 2.07 million were assigned ASJC codes in Scopus corresponding to Computer Science (major subject area with 13 minor subject areas (Table~\ref{tab:comp}), with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (Fig.~\ref{fig:ar_cp_annotation}). The set of 2.07 million publications classified under the major subject area Computer Science in Scopus spanned all 13 minor subject areas with Software 30.3\% being the largest component and Computer Science (miscellaneous) 0.9\% the smallest. Interestingly, 409,082  publications were labeled Theoretical Computer Science but under the major subject area of Mathematics(Table~\ref{tab:comp}). Overall, 38.86\% of the publications were assigned to one minor subject area, 78.1\% to two minor subject areas, 909.9\% to three minor subject areas, and 0.0003\% assigned to 8 different minor subject areas.
